\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.

\makeatletter
\def\lst@makecaption{%
  \def\@captype{table}%
  \@makecaption
}
\makeatother

\input{./Files/util.tex}

\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}


\begin{document}

\title{\tool: Revisiting BadUSB with Type-C}

\author{Anonymous Authors}
%\author{\IEEEauthorblockN{1\textsuperscript{st} Given Name Surname}
%\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
%\textit{name of organization (of Aff.)}\\
%City, Country \\
%email address or ORCID}
%\and
%\IEEEauthorblockN{2\textsuperscript{nd} Given Name Surname}
%\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
%\textit{name of organization (of Aff.)}\\
%City, Country \\
%email address or ORCID}
%\and
%\IEEEauthorblockN{3\textsuperscript{rd} Given Name Surname}
%\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
%\textit{name of organization (of Aff.)}\\
%City, Country \\
%email address or ORCID}
%\and
%\IEEEauthorblockN{4\textsuperscript{th} Given Name Surname}
%\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
%\textit{name of organization (of Aff.)}\\
%City, Country \\
%email address or ORCID}
%\and
%\IEEEauthorblockN{5\textsuperscript{th} Given Name Surname}
%\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
%\textit{name of organization (of Aff.)}\\
%City, Country \\
%email address or ORCID}
%\and
%\IEEEauthorblockN{6\textsuperscript{th} Given Name Surname}
%\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
%\textit{name of organization (of Aff.)}\\
%City, Country \\
%email address or ORCID}
%}

\maketitle
\thispagestyle{plain}
\pagestyle{plain}


\newacro{USB}{Universal Serial Bus}
\newacro{HID}{Human Interface Device}
\newacro{UI}{User Interface}
\newacro{PnP}{Plug-and-Play}
\newacro{OEM}{Original Equipment Manufacturer}
\newacro{DoS}{Denial of Service}
\newacro{MHL}{Mobile High-Definition Link}
\newacro{URB}{USB Request Block}
\newacro{OCR}{Optical Character Recognition}
\newacro{GUI}{Graphical User Interface}

\begin{abstract}

The security of the \ac{USB} protocol has been paid extensive attention to because of its
    wide usage.  Due to the \textit{trust-by-default} characteristics, \ac{USB}
    security has caused severe problems.  For example, a well-known firmware
    attack, BadUSB, performs malicious operations on the victim hosts through
    disguising ordinary \ac{USB} devices as human interface devices like keyboards and
    mice.  However, BadUSB suffers from several limitations.  Attackers cannot
    obtain the status of \ac{UI} to conduct precise attacks and get the visual feedback of their attacks.  In this work, we
    extended BadUSB to support the new \ac{USB} Type-C features and proposed a
    multi-mode attack model, \tool.  It obtains UI status to make attacks more 
    precise and effective.  To the best of our knowledge, \tool is the first attack model
    utilizing \ac{USB} Type-C.  To validate the usability and effectiveness, we
    conducted extensive experiments and a user study on a real-life attack
    scenario.  10 volunteers are involved in, and 4,172 of 94,058 records
    obtained by \tool in the user study are related to sensitive information.
%\fengwei{What results?} \fengwei{what countermeasures do we propose? including
    %isolated UI rendering.}
We also discussed the recommended countermeasures for our attack model,
    including isolated UI rendering, which may be inspiring for future research
    on defense methods.
\end{abstract}

\begin{IEEEkeywords}
USB; BadUSB; Type-C; Attack
\end{IEEEkeywords}


\acresetall

\input{./Files/introduction.tex}
\input{./Files/background.tex}
\input{./Files/related_work.tex}
\input{./Files/badusb.tex}
\input{./Files/experiment.tex}
\input{./Files/countermeasure.tex}
\input{./Files/discussion.tex}
\input{./Files/conclusion.tex}
%\input{./Files/acknowledgement.tex}





\balance

\bibliographystyle{IEEEtran}
\bibliography{BadUSBC}


\end{document}
